An Investigation of Confusing Code Patterns in JavaScript

### 2023-04-04 discussion.tex
cr candidate

\textbf{Logic as Control Flow} is a more interesting case. Considering the correctness perspective, none of our experiments has identified Logic as Control Flow as an atom of confusion. However, in the Latin square study there was a significant difference in the time required to make a correct prediction in favor of the clean version of this atom candidate, with a medium effect size. Furthermore, both Langhout and Aniche~\cite{Langhout:2021:ACJ} and Gopstein and colleagues~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17} have identified it as an atom. Two other atoms have exhibited a statistically significant difference in time, in favor of their obfuscated versions (with a small effect size). One of them, \textbf{Pre-Increment}, has been confirmed as an atom of confusion in multiple experiments, i.e., participants are less confused by the clean versions. These conflicting results reinforce the importance of conducting experiments that consider multiple response variables~\cite{Oliveira:2020:ECR}. In addition, it is clear that factors such as the experience of the participants and the selection of code snippets can have considerable impact on the results of studies about code readability~\cite{Feitelson:2021:CPC}. \revised{Table~\ref{tab:summary-of-findings} summarizes the correctness assessment results in our two experiments (columns Exp01 and Exp02) and the experiments of
Gopstein et al.~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17} and Langhout and Aniche~\cite{Langhout:2021:ACJ}.}

@@

\begin{table}
  \caption{Results of the exploratory data analysis for the experiments (Repeated Measurea and Latin Square)}
  \label{tab:merge-exploratory-study}
  \begin{scriptsize}
  \begin{tabular}{lccccc} \toprule
                                 & \multicolumn{2}{c}{Repeated Measures} & \multicolumn{2}{c}{Latin Square} & \\  
  Atom Candidate                 &   Obfuscated   &   Clean   &   Obfuscated   &   Clean   &  $\Delta$ (\%)    \\ \midrule
Comma Operator                   &      8         &   29      &       28       &     65    &   161.11  \\
Automatic Semicolong Insertion   &     15         &   21      &       32       &     68    &    89.36  \\
Assignment as Value              &     18         &   43      &       56       &     68    &    50.00  \\
Post-Increment                   &      8         &   17      &       48       &     64    &    44.64  \\
Omitted Curly Braces             &     35         &   51      &       47       &     58    &    32.92  \\
Pre-Increment                    &     13         &   28      &       50       &     53    &    28.57  \\
Implicit Predicate               &     41         &   44      &       58       &     68    &    13.13  \\
Conditional Operator             &     60         &   62      &       60       &     66    &     6.66  \\
Logic as Control Flow            &     33         &   28      &       41       &     48    &     2.70  \\ 
Arithmetic as Logic              &     52         &   47      &       64       &     63    &    -5.17  \\ \bottomrule
  \end{tabular}
\end{scriptsize}  
\end{table}

>>>>

\textbf{Logic as Control Flow} is a more interesting case. Considering the correctness perspective, none of our experiments has identified Logic as Control Flow as an atom of confusion. However, in the Latin square study there was a significant difference in the time required to make a correct prediction in favor of the clean version of this atom candidate, with a medium effect size. Furthermore, both Langhout and Aniche~\cite{Langhout:2021:ACJ} and Gopstein and colleagues~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17} have identified it as an atom. Two other atoms have exhibited a statistically significant difference in time, in favor of their obfuscated versions (with a small effect size). One of them, \textbf{Pre-Increment}, has been confirmed as an atom of confusion in multiple experiments, i.e., participants are less confused by the clean versions. These conflicting results reinforce the importance of conducting experiments that consider multiple response variables~\cite{Oliveira:2020:ECR}. In addition, it is clear that factors such as the experience of the participants and the selection of code snippets can have considerable impact on the results of studies about code readability~\cite{Feitelson:2021:CPC}. \revised{Table~\ref{tab:summary-of-findings} summarizes the correctness assessment results in our two experiments: Repeated Measures Study (column Exp01) and Latin Squares Study (column Exp02) and the experiments of
Gopstein et al.~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17} and Langhout and Aniche~\cite{Langhout:2021:ACJ}.}

@@

\begin{table}
  \caption{Results of the exploratory data analysis for the experiments (Repeated Measures and Latin Squares design). The Obfuscated and
    Clean columns show the number of correct answers for the obfuscated and clean versions of the code samples in both experiments. We compute the {\bf total} number of correct answers for the obfuscated
    version of the code in both experiments (TO) and the {\bf total} number of correct answers for the clean version of the code in
    both experiments (TC). The $\Delta$ column is given by $\Delta = \frac{TC - TO}{TO}$.}
  \label{tab:merge-exploratory-study}
  \begin{scriptsize}
  \begin{tabular}{lcccc|ccc} \toprule
                                 & \multicolumn{2}{c}{Repeated Measures} & \multicolumn{2}{c}{Latin Square} & \\  
  Atom Candidate                 &   Obfuscated   &   Clean   &   Obfuscated   &   Clean   & TO  & TC  & $\Delta$ (\%)    \\ \midrule
Comma Operator                   &      8         &   29      &       28       &     65    & 36  & 94  & 161.11  \\
Automatic Semicolong Insertion   &     15         &   21      &       32       &     68    & 47  & 89  & 89.36  \\
Assignment as Value              &     18         &   43      &       56       &     68    & 74  & 111 & 50.00  \\
Post-Increment                   &      8         &   17      &       48       &     64    & 56  & 81  & 44.64  \\
Omitted Curly Braces             &     35         &   51      &       47       &     58    & 82  & 109 & 32.92  \\
Pre-Increment                    &     13         &   28      &       50       &     53    & 63  & 81  & 28.57  \\
Implicit Predicate               &     41         &   44      &       58       &     68    & 99  & 112 & 13.13  \\
Conditional Operator             &     60         &   62      &       60       &     66    & 120 & 128 &  6.66  \\
Logic as Control Flow            &     33         &   28      &       41       &     48    & 74  & 76  & 2.70  \\ 
Arithmetic as Logic              &     52         &   47      &       64       &     63    & 116 & 110 & -5.17  \\ \bottomrule
  \end{tabular}
\end{scriptsize}  
\end{table}

### 2023-04-04 s04.tex
cr candidate

We mine a set of GitHub open source repositories and compute how often these atom candidates occur. We do this with the goal of quantifying the prevalence of the investigated atom candidates. \revised{If they rarely occur in real-world systems, this would suggest that cannot be a significant source of confusion for developers. This study addresses our first research question (\emph{What is the frequency of occurrence of atom candidates in practice?}).}

@@

After filtering out JavaScript project candidates, we build a curated dataset comprising a total of \minedprojects repositories. Examples of projects in this dataset include \textsc{React}, \textsc{Node JS}, and \textsc{AngularJS}. Table~\ref{tab:projects-statistics} presents some statistics about the projects we consider in our research. The size of the projects range from small ones (5543 lines of code) to complex systems with more than 1 MLOC. All projects in our dataset have at least \num[group-separator = {,}]{1244} forks and at least \num[group-separator = {,}]{23672} stars. We automate all the steps to filter, clone, and collect the statistics from the repositories using Python scripts.

>>>>

We mine a set of GitHub open source repositories and compute how often these atom candidates occur. We do this with the goal of quantifying the prevalence of the investigated atom candidates. \revised{If they rarely occur in real-world systems, this would suggest that they cannot be a significant source of confusion for developers. This study addresses our first research question (\emph{What is the frequency of occurrence of atom candidates in practice?}).}

@@

After filtering out JavaScript project candidates, we build a curated dataset comprising a total of \minedprojects repositories. Examples of projects in this dataset include \textsc{React}, \textsc{Node JS}, and \textsc{AngularJS}. Table~\ref{tab:projects-statistics} presents some statistics about the projects we consider in our research. The size of the projects range from small ones (5,543 lines of code) to complex systems with more than 1 MLOC. All projects in our dataset have at least \num[group-separator = {,}]{1244} forks and at least \num[group-separator = {,}]{23672} stars. We automate all the steps to filter, clone, and collect the statistics from the repositories using Python scripts.
